Diversity dynamics in Nymphalidae butterflies: Effect of phylogenetic uncertainty on diversification rate shift estimates

### 2014-11-04 response_to_reviewers.tex

\textbf{4. Reviewer's Comment:}

Why are they restricting their analysis to only one method (a method
that they point out might not be reliable)? There are alternative
methods available, and it might be interesting to see if consistent
results are observed (eg., RC, PRC, BAMM). There is very little
development on other aspects of plant -- herbivore interactions and how
they might be predicted to affect diversification rate.

\textbf{4. Response:}

\begin{quote}
\color{blue}
The methods RC and PRC (parametric rate comparison and relative rates tests) 
fit several distribution models to the trees in order to
infer branch lengths. This requires random sampling of taxa to avoid biases.
This assumption is not satisfied with our data as the sampling is non-random.
This is one of the characteristics of butterfly datasets where many geographic
areas are not sampled leaving out major lineages.

@@

The method that we used, BiSSE, might not be reliable when the number of
taxa is small, and there are biases in the number of species that have
each of the character states. However, we stated in the manuscript that
according to the evaluation of BiSSE by Davis, Midford, and Maddison
(2013), our data should not be affected for such biases.

The method BAMM can be used to explore the evolution of phenotypic
traits. However the trait characters
\href{http://bamm-project.org/configuration.html\#id5}{\textbf{must be
continuous}}. In our case the ``feeding on Solanaceae plants'' trait is
categorical (absence/presence) so it cannot be analyzed with BAMM.

BAMM also measures the diversification rates of particular clades. We
run an analysis to test whether we obtained congruent results. In the
Fig. 1, shown below, we can see that BAMM was able to pick up two
increases in diversification for Ithomiini butterflies, one for the
origin of the clade and, most importantly, another increase during the
recent diversification of the group. This is in agreement with our
results from using BiSSE, that the ithomiines using Solanaceae underwent
an increase in diversification rates.

We added to the revised version of the MS that we also ran BAMM in order to
test congruence of the results with this recent menthods.
\end{quote}

### 2014-11-04 MS_revised.tex
2nd run bamm

>>>>

We contrasted these results with those obtained from analysing the data in
the software BAMM. We found 
that the best model (best configuration) estimated 8 diversification shifts in
our MCC tree (posterior probability = 0.65). Bayes factor values strongly 
favored this model in comparison with the second best model (7 diversification
shifts, BF > 37,000). <<<<CHECK AGAIN AFTER 2nd BAMM Run >>>
